\chapter{SYSTEM ANALYSIS }
 
 \section{Module Description}
 The LAVA ESPORTS platform is divided into multiple functional modules, each supporting navigation, data management, and role-based workflows. The main modules include:
 \begin{itemize}
    \item \textbf{Authentication \& Authorization Module:} Handles registration, login, email verification flow, session management, and role-aware route access.
    \item \textbf{Team Management Module:} Provides team listing, team detail views, and application workflows for authenticated users.
    \item \textbf{Event Tracking Module:} Supports event listing, event detail pages, and authenticated registration/unregistration.
    \item \textbf{Recruitment Module:} Exposes public recruitment listings and recruiter-only creation of recruitment posts.
    \item \textbf{Admin Panel Module:} Provides administrative user management and CRUD management for events and teams.
\end{itemize}

\section{Business Rules}
Business rules are specific guidelines, conditions, or constraints that govern the operations of a system. They define how processes and activities should be conducted to ensure consistency, fairness, and alignment with business objectives.

\textbf{User Management}
\begin{itemize}
    \item All users must authenticate before accessing personalized dashboard features.
    \item Passwords must be securely hashed before storage in the database to ensure user privacy and protection.
    \item Only users with administrative privileges can access the Admin Panel and alter global event or team data.
    \item Only recruiter-role users can create recruitment posts.
\end{itemize}
\textbf{Team \& Event Operations}
\begin{itemize}
    \item Events must have a valid scheduled date before they can be published on the platform.
    \item Authenticated users may register for events and apply to teams.
    \item Application moderation (accept/reject) requires authenticated privileged access.
\end{itemize}

\newpage
 \section{Analysis of Architecture}
{\large \textbf{Laravel Framework}}

Laravel is a powerful PHP framework utilized for constructing the robust backend architecture of LAVA ESPORTS. It provides a structured foundation based on the Model-View-Controller (MVC) paradigm, ensuring clean separation of concerns and maintainable code.
\begin{enumerate}
    \item \textbf{Routing and Controllers:}
    \begin{itemize}
        \item Matches incoming HTTP requests to corresponding controller actions, streamlining page navigation and API responses.
    \end{itemize}
    \item \textbf{Eloquent ORM:}
    \begin{itemize}
        \item Provides an elegant active record implementation for interacting with relational databases, simplifying queries and schema relationships.
    \end{itemize}
    \item \textbf{Blade Templating Engine:}
    \begin{itemize}
        \item Generates dynamic HTML user interfaces by combining standard HTML markup with dynamic PHP data, allowing for modular UI components like navigation bars and sidebars.
    \end{itemize}
\end{enumerate}

\section{System Environment}
 
 \subsection{Software Environment}
 \textbf{Laravel 12 (Backend):}
 The core server-side development of LAVA ESPORTS is built upon Laravel 12. It manages routing, user authentication, Eloquent models, and database migrations.
 
 \textbf{Tailwind CSS v4 (Frontend Styling):}
 Relied upon heavily for utility-first styling, ensuring responsive layouts, dynamic hover effects, and a highly customizable dark-mode aesthetic.
 
 \textbf{Alpine.js (Frontend interactivity):}
 Enhances the Blade templates with lightweight JavaScript behavior, handling dynamic UI states such as modals, dropdowns, and responsive sidebar toggles.

 \textbf{PostgreSQL (Database):}
 Primary target relational database for production workloads, used to store and manage user credentials, team rosters, and event data.
 
 \subsection{Hardware Environment (Recommended Server Specs)}
 \textbf{Processor (CPU):} 2+ Cores (e.g., Intel Xeon or AWS EC2 equivalent)\\
 \textbf{Memory (RAM):} 4 GB minimum\\
 \textbf{Storage:} 40 GB SSD\\
 \textbf{Operating System:} Linux (Ubuntu 22.04 LTS or similar)

 \newpage
 
 \section{Actors and Roles}
 The system involves three primary actors:\\\\
 \textbf{Actor Name: User}\\
 \textbf{Role:} General users who browse events and teams, register for events, and apply to teams.
 
 \textbf{Actor Name: Administrator}\\
 \textbf{Role:} Platform overseers equipped with complete CRUD capabilities via the Admin Panel to manage platform data securely.
 
 \textbf{Actor Name: Recruiter}\\
 \textbf{Role:} Specialized users who publish recruitment posts and scout emerging eSports talent.
